% !TeX spellcheck = en_US
%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Jason}{Huang}
\title{Curriculum Vit\ae}                               % optional, remove / comment the line if not wanted
\address{4301 Romfield Cres}{L5M 4L4 Mississauga}{Canada}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~(647)~631~6610}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\phone[fixed]{+1~(416)~499~9018887}
%\phone[fax]{+3~(456)~789~012}
\email{jasonhuang@disroot.org}                               % optional, remove / comment the line if not wanted
\homepage{jasonhuang.netlify.com}                         % optional, remove / comment the line if not wanted
\social[linkedin]{jasonhuang03}                        % optional, remove / comment the line if not wanted
\social[twitter]{jhthenerd}                             % optional, remove / comment the line if not wanted
\social[github]{jhthenerd}                              % optional, remove / comment the line if not wanted
%\social[gitlab]{jhthenerd}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\quote{Life is the ultimate optimization problem}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Karen Knight}{Queen's School of Computing\\25 Union Street\\Goodwin Hall, Room 557\\Kingston, Ontario K7L 3N6}
\date{\today}
\opening{Dear Ms. Knight,}
\closing{Yours faithfully,}
\enclosure[Attached]{curriculum vit\ae{}, reference letters}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

% Details your interest in the subject (CS), experience in desired area of study

I am Jason Huang, a high school student in Grade 11.
I am interested in the field of computing, specifically software design,
and have pursued this subject both at school as well as on my own time.

I first started programming in middle school, and have continued to work on side projects and learn new technologies as I grew older. 
I started attending hackathons in high school, and have gone to events like Hack the North, where I learned how to work with a team to create a realistic product in a limited timeframe.

Around this same time, I became interested in Linux, both for development and as a general-purpose operating system.
Using Linux has encouraged me to understand the inner workings of my operating system, and has introduced me to technologies like copy-on-write filesystems different types of kernels.

Recently, I have become interested in the field of information security.
I competed in PicoCTF with a few of my friends, which taught me a lot about various technologies and tools used in the security field, as well as how programs worked and communicated with hardware at a low level.

Aside from exploring computer science on my own time, I have also taken some courses at school.
I have taken my school's grade 10 computer studies course, finishing with a 98\%, as well as the grade 11 computer science course, finishing with a 100\%
Furthermore, I have also taken the AP Computer Science 1 exam, and achieved a perfect 5/5.
I also recently took the CCC Senior contest, finishing with a score of 33.

I have also looked to strengthen my mathematical skills, and thus have taken up to grade 12 Calculus and Vectors outside of school, and am currently preparing for the AP Calculus BC exam. 

I believe that my experience with software design and mathematics, combined with my interest in various computing topics makes me an excellent candidate for this internship position.

\makeletterclosing

\clearpage


%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2017--Present}{High School}{John Fraser Secondary School}{Mississauga}{\textit{94\%}}{}  % arguments 3 to 6 can be left empty
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}

%\section{Master thesis}
%\cvitem{title}{\emph{Title}}
%\cvitem{supervisors}{Supervisors}
%\cvitem{description}{Short thesis abstract}

\section{Experience}
%\subsection{Vocational}
\cventry{2017--2019}{Volunteer}{Central Library}{Mississauga}{}{Computer Buddies program member, general volunteer.% \newline{}%
%Achievements:%
	\begin{itemize}
		\item Communicate and teach older adults basic computer skills
		\item Work with clients to solve unique problems
		\item Maintain and help improve the experience for library patrons
	\end{itemize}
}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description}

\section{Clubs}
\cventry{2018--Present}{Executive}{Computer Science Club}{John Fraser SS}{}{
	\begin{itemize}
		\item Taught other students advanced programming concepts
		\item Worked with other executives to promote computer science education
		\item Helped run a hackathon at John Fraser
	\end{itemize}
}
\cventry{2017--Present}{Co-founder}{3D Printing Club}{John Fraser SS}{}{
	\begin{itemize}
		\item Primary maintainer of 3D printers and related software
		\item Work within the school to promote and educate peers about 3D printing technology
		\item Train and educate younger members on best practices and maintenance
		\item Advise teachers on various materials and printers
		\item Collaborate with teachers to introduce 3D printing into the curriculum
	\end{itemize}
}
\cventry{2017--Present}{Lead Engineer}{VEX Robotics}{John Fraser SS}{}{
	Team 82050A
	\begin{itemize}
		\item Built, troubleshooted, and maintained robot hardware
		\item Collaborated with rest of team to resolve issues
		\item Worked with other high-ranking team members to recruit and vet new members
		\item Made it to provincials in 2019-2020 season
	\end{itemize}
}

\section{Honors \& Awards}
\cvitemwithcomment{2019}{Canadian Intermediate Math Contest (CIMC) School Champion}{John Fraser SS}
\cvitemwithcomment{2018}{Best Highschool Hack}{Redbull AdrenaLAN 2018}
%\cvitemwithcomment{Achievement in <Grade 9 Science - Advanced Placement}{John Fraser Secondary School}{2018}

%\newpage

\section{Projects}
\cventry{2019}{Dr. Dash}{}{Hack the North}{}{
	\url{https://github.com/davidli3100/HTN2019}
	\begin{itemize}
		\item A chatbot that helps patients submit pertinent information to doctors before their appointment, that interfaces with voice assistants, Facebook Messenger, and telephony
		\item Built with 3 other people during Hack the North
		\item Built using Firebase and DialogFlow
	\end{itemize}
}
\cventry{2019--Present}{FraserConnect}{}{John Fraser SS}{}{
%	\url{}
	\begin{itemize}
		\item An interface allowing students to receive announcements, event updates, and polls from JFSS
		\item Developed using React Native with a Firebase server
	\end{itemize}
}
\cventry{2019--Present}{OpenDo}{}{Personal}{}{
	\begin{itemize}
		\item A open-source todo application with both a GUI and CLI frontent
		\item Built using Go
	\end{itemize}
}
\cventry{2018--2019}{FraserHacks 2019 Website}{}{John Fraser SS}{}{
	\url{https://github.com/FraserHacks/FraserHacks-Website}
	\begin{itemize}
		\item A website promoting FraserHacks 2019
		\item A collaborative project completed with a team of 2 other people
		\item Developed in pure HTML, CSS, JS
	\end{itemize}
}

\section{Events Hosted}
\cventry{2019}{FraserHacks}{John Fraser SS}{Mississauga}{}{
	A hackathon for high school students in Peel, run during school hours. \\
	First such event run in Fraser.\\
	Responsibilities:
	\begin{itemize}
		\item Build and update hackathon website
		\item Find and assess potential team members
		\item Work with school administration to plan and organize logistics
		\item Help run AV equipment and events on-site
	\end{itemize}
}

\section{Achievements}
\cvitemwithcomment{2019}{SAT Physics (770)}{The College Board}
\cvitemwithcomment{2019}{AP Physics A (5)}{The College Board}
\cvitemwithcomment{2019}{AP Computer Science A (5)}{The College Board}
\cvitemwithcomment{2018}{SAT (1530)}{The College Board}

\section{Skills}
\subsection{Operating Systems}
\cvitem{Windows}{Understanding of system, command-line usage, administration.}
\cvitem{Linux}{Over 2 years of experience using Linux for development and casual use.}

\subsection{Development Tools}
Have extensive experience with Git for both personal and collaborative projects.

Have experience with managing Linux and BSD servers.

Have experience with virtualization and containerization, using tools like VirtualBox, KVM, Docker

\newpage

\subsection{Programming Languages}
Over 3 years of experience in C++, Java, Javascript.

Comfortable using Python, \LaTeX, Go.

Currently learning Rust.

\subsection{Frameworks}
\cvitem{React / React Native}{A Node.js based framework that allows for HTML to be componentised. Have had experience using React for both hackathon and team projects.}

\subsection{Soft Skills}
\cvitem{Organization}{Uses various tools such as task managers and calendars to keep track of tasks from various classes and projects}
\cvitem{Leadership}{Has helped lead various teams to coordinate and colaborate on difficult tasks}
\cvitem{Communication}{Expresses ideas and concerns to peers, while remaining open to suggestions and potential improvements. Fosters a relaxed group atmosphere.}

\subsection{Strong Academic Subjects}
\cvitem{Computer Science}{Has taken both grade 10 and grade 11 computer science, achieving a 98\% and 100\% respectively. Has self-studied various languages and technologies out of personal interest.}
\cvitem{Physics}{Has taken grade 11 AP physics, achieving a 96\%. Has also self-studied grade 12 physics, and taken extracurricular classes for grade 12 physics.}
\cvitem{Math}{Finished grade 10 AP math with 96\% average , currently taking grade 11 AP math, has taken extracurricular Advanced Functions, Calculus, and AP Calculus}

%\cvdoubleitem{Operating Systems}{Windows, Linux (Debian-based, RPM-based)}{Development Tools}{VS Code, Vim, Git}
%\cvdoubleitem{Languages}{C++, Java, Javascript}{Soft Skills}{Organization, Leadership, Communication}
%\cvdoubleitem{Frameworks}{React, React Native}{Strong Subjects}{Computer Science, Physics, Math}


\section{Interests}
\cvitem{CTFs}{Short for Capture The Flag, CTFs are a competitive infosec challenge where competitors use various red-team techniques to gain access to a flag, usually in the form of a short text snippet}
\cvitem{Photography}{Does casual photography for family and occasionally posts photos online}
\cvitem{Linux}{Uses Linux on daily driver laptop, and enjoy using and modifying the system during free time}

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}
%
%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

\section{References}
See attached reference letters
%\begin{cvcolumns}
%  \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%  \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%  \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
%\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file


%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
